Letter of Inquiry For Holier Than Thou: Partisan Gap in the Consumption of Pornography Online

### 2024-04-15 ms/scrap_yard.tex
Updates from Overleaf (#3)
resolving merge conflict...

@@

>>>>

\subsubsection{Percentage of Time Spent on Top 10 Most Visited }

%===========================================================================
% Tabulated splits by party and by percentiles for hours spent on adultsites
%===========================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online by Party (\texttt{piedomains})}
	\label{tab:piedomains_distribution_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{tabs/piedomains_percentiles_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		The table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		Classification of pornography sites is based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
		See \cref{tab:piedomains_distribution_prop_duration_party} for the corresponding distribution in terms of percentage of time. 
		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.0481, rejecting the null that the Republican and Democrat distributions are the same at the 5\% level.
		%See \cref{fig:distribution_duration_party} for the plot.
	}
\end{table}

%===============================================================================
% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
%===============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites by Party (\texttt{piedomains})}
	\label{tab:piedomains_distribution_prop_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{tabs/piedomains_percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		The table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period. 
		Classification of pornography sites is based on a machine learning classifier \citep{Chintalapati_piedomains_Predict_the_2022}.
		See \cref{tab:piedomains_distribution_duration_party} for the corresponding distribution in terms of percentage of time.
		A two-sample Kolmogorov–Smirnov test returns a p-value of 0.19, failing to reject the null that the Republican and Democrat distributions are the same at the 5\% level.
		%See \cref{fig:distribution_prop_duration_party} for the plot.
	}
\end{table}

%====================================
% Figure of traffic to top x websites
%====================================
\begin{figure}[h]
	\centering
	\caption{Traffic to Top x Pornographic Sites by Party}
	\includegraphics[width=.6\textwidth]{figs/concentration_porn_consumption_topX_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		The figure shows the concentration of pornography consumption based on individuals' most frequented pornographic sites.
            The underlying data is the individual's own most frequented site.
            We first sort online pornography sites for each individual and compute the percentage of time that individual spent for his/her own top 10 sites before computing and plotting the average (as shown above).
		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption_topX_by_party}
\end{figure}

\begin{figure}[ht]
\caption{Time Spent on Online Pure Pornography vs. Adult-related Leisure}
\label{fig:tu_prop_adult_entertainment-prop_pure_adult}
     \centering
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/tu_duration_adult_entertainment-duration_pure_adult.pdf}
         \caption{Entertainment}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.495\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figs/tu_duration_adult_shop-duration_pure_adult.pdf}
         \caption{Shopping}
     \end{subfigure}
\caption*{\footnotesize \emph{Notes:}
Lowess for time spent on online pornography (excludes adult entertainment, adult gaming, adult shopping) vs time spent on other adult-related leisure (``adult entertainment'' and ``adult shopping'').
Observations above the 90th percentile are omitted. 
Adult-related entertainment sites are those with YouGov categories containing ``adult'' and ``entertainment''---top five of such sites are thechive.com, redgifs.com, 4chan.org, hentairead.com, and hentaifox.com. Adult-related shopping sites are those with YouGov categories containing ``adult'' and ``shopping''---top five of such sites are manyvids.com, adameve.com, victoriassecret.com, honeyplaybox.com, and r18.com. Each estimation in the Lowess uses half of the sample data. The 95\% confidence intervals shaded in blue are bootstrapped (n = 1000).}
\end{figure}

@@

%====================================
% Figure of traffic to top x websites
%====================================
\begin{figure}
	\centering
	\caption{Traffic to Top x Pornographic Sites by Party}
	\includegraphics[width=.6\textwidth]{../figs/concentration_porn_consumption_topX_by_party.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows concentration of pornography consumption based on individuals' most frequented pornographic sites.
		Shaded areas are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:concentration_porn_consumption_topX_by_party}
\end{figure}
